---
title: "Final Report"
author: "Tweets6 - Naramol Pipoppinyo, Risa Yamazaki, Thanh Dat Nguyen, Eran Kan Kohen and Abdukarim Omar"
date: "2023-06-07"
output:
  bookdown::html_document2:
    toc: yes
    toc_float:
      collapsed: no
    number_sections: yes
    theme: cosmo
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Introduction**

With the rise of social media, many organizations have used these online
platforms to establish a new communication channel with potential
customers. Thanks to the bidirectional nature of these platforms, users
of sites such as Twitter, Facebook, and Instagram are not not just
passive consumers of content but can also actively express their
thoughts and opinions on content that these organizations create. Some
companies attempt to make use of this unique feature of social media by
pursuing novel approaches to marketing in hopes of gaining a competitive
advantage. One of these approaches to online marketing communication is
brand anthropomorphism, where companies engage in human-like
company-consumer communication and relationship building that goes
beyond the traditional brand image. Since the emergence of the strategy,
there are an increasing number of corporations across various industries
that make the shift from traditional "objectified brands" that construct
an autonomous brand image to brands with more anthropomorphic features
to improve brand perception and build new connections with consumers.
The study by Delgado-Ballester et al. (2019), investigated consumer's
general sentiment for apparel brands in experimental form demonstrated
that humanized clothing brands were more effective than objectified
brands in fostering the positive brand perceptions and emotional
connections with consumers, even though that the effectiveness is
dependent on the question of whether consumers would prefer to see the
specific brand acting like a human. Such effect of anthropomorphism of
brands is also visible on the social media in the form of direct
consumer engagement with the brand's official accounts. A supervised
machine learning study revealed that consumers engage more with
humanized content posted by companies and dialogic replies (Wu et al.,
2023). However, the study used the count of Twitter activities (e.g.
replies counts, retweets) as the metrics of engagement of consumers,
while the online sentiments of consumers towards those anthropomorphized
accounts remain unclear, which calls for deeper research of the contents
of consumers responses.

This study will expand upon the study conducted by Delgado-Ballester et
al. (2019) by focusing on specifically the aviation industry. The
aviation industry is a very particular industry since the main service
they provide is one that people keep on purchasing even though 40% of
the population is scared of flying (Schaaff, 2019). Therefore, they
focus maintaining positive customer experience inside and outside of the
aircraft. As an industry that provides customers services, customer
engagement that leads to the growth in brand equity is significant
(Foxall, 2019). Companies from this industry, therefore, constantly seek
effective social marketing strategies and implement them to enhance
brand visibility and reputations (Foxal, 2019). Since Delgado-Ballester
et al. (2019) did not focus on any company from the aviation industry in
their study regarding anthropomorphic social media presences, this study
will aim to fill in that gap.The explored results delivered in this
study is expected to add insights on the strategic brand positionings
for aviation companies.

To conduct a comprehensive analysis of the effects and implications
associated with implementing an anthropomorphic social media strategy,
it was essential to compare brands that exhibit similar Tweeting
frequencies and share geographical similarities. Initially, Ryanair was
selected as the anthropomorphic brand. With over 720 thousand followers
and an organizationally verified [Twitter
account](https://twitter.com/Ryanair?ref_src=twsrc%5Egoogle%7Ctwcamp%5Eserp%7Ctwgr%5Eauthor)
the Irish company's social media presence has received high praise (Loh,
2023). They are known for writing Tweets in a funny, rude, and overall
human-like way (Schlappig, 2022). Besides Ryanair, the anthropomorphized
group also included United Airlines, who similarly use their Twitter
account to engage more in customer dialogue. An example Tweet can be
found
[here](https://twitter.com/united/status/1664296946880724993?s=20). For
the comparison, we selected airline companies, which used their Twitter
accounts in a more professional, objectified manner. This included
Emirates, Qatar, United, Turkish Airlines and EasyJet. Thus, Ryanair and
United will be compared with Emirates, Qatar, Turkish, and EasyJet.

As a service industry, aviation companies must be successful with
maintaining positive sentiments among customers by leveraging
communication strategies, while not depriving trusts among consumers
about the quality of service. This study will aim to see if either the
sentiment or the quantity of interactions differ among the selected
Twitter accounts.

Therefore, we chose the companies to compare the consumer's online
response and sentiments with a research question, "What is the effect of
brand anthromorphism on social media engagement for aviation industry?"
This research question would help the aviation industry to understand
online consumer behavior and utilize it for their strategic positioning.

The research question will be answered by addressing sub research
questions as follows;

-   How does brand anthropomorphism affect the number of likes,
    re-tweets, replies on Twitter?

-   How does brand anthropomorphism affect the sentiments of consumers
    on Twitter?

-   Does brand anthropomorphism have an interaction effect on the
    sentiment and interaction metrics on Twitter?

This study serves mostly as an exploratory study into the effects of
brand anthropomorphism on the engagement metrics of the aviation
industry, and does not attempt to assert causal relationships between
these variables.

# **Data Collection and Processing**

```{r, child=here::here("sections", "Data Collection.Rmd")}
```

# **Data Analysis**

```{r, child=here::here("sections", "Data Processing and Analysis.Rmd")}
```

# **Conclusions and Implications**

```{r, child=here::here("sections", "Conclusions and Implications.Rmd")}
```

# **Limitations and Future Improvements**

```{r, child=here::here("sections", "Limitations.Rmd")}
```

## **References**

Abdullah, N. A., Nishioka, D., Tanaka, Y., & Murayama, Y. (2015). User's
action and decision making of retweet messages towards reducing
misinformation spread during disaster. *Journal of Information
Processing*, *23*(1), 31--40. <https://doi.org/10.2197/ipsjjip.23.31>

Azar, S., Machado, J. C., Vacas-De-Carvalho, L., & Mendes, A. M. (2016).
Motivations to interact with brands on Facebook -- Towards a typology of
consumer--brand interactions. *Journal of Brand Management, 23*(2),
153--178. <https://doi.org/10.1057/bm.2016.3>

Delgado-Ballester, E., Palazon, M., & Peláez, J. M. M. (2019).
Anthropomorphized vs objectified brands: which brand version is more
loved? *European Journal of Management and Business Economics, 29*(2),
150--165. <https://doi.org/10.1108/ejmbe-04-2019-0063>

Foxall, G. R. (2018). An economic psychology of the marketing firm. In
A. Lewis (Ed.), *The Cambridge Handbook of Psychology and Economic
Behaviour* (2nd ed., pp. 365--402). Cambridge University Press.
<https://doi.org/10.1017/9781316676349.013>

Hayes, A. F., & Montoya, A. K. (2017). A Tutorial on Testing,
Visualizing, and Probing an Interaction Involving a Multicategorical
Variable in Linear Regression Analysis. *Communication Methods and
Measures, 11*(1), 1--30. <https://doi.org/10.1080/19312458.2016.1271116>

Kim, T. K. (2015). T test as a parametric statistic. *Korean Journal of
Anesthesiology*, *68*(6), 540.
<https://doi.org/10.4097/kjae.2015.68.6.540>

Loh, C. (2023, April 29). *Controversial yet entertaining: Examining
ryanair's social media strategy*. Simple Flying.
<https://simpleflying.com/ryanair-social-media-strategy/>

Mochon, D., Johnson, K., Schwartz, J., & Ariely, D. (2017). What Are
Likes Worth? A Facebook Page Field Experiment. *Journal of Marketing
Research*, *54*(2), 306--317. <https://doi.org/10.1509/jmr.15.0409>

Parilla-Ferrer, B.E., Fernandez, P.L., & Ballena, J.T. (2015). Automatic
classification of disaster-related tweets. (2014, December 28).
<https://www.semanticscholar.org/paper/Automatic-Classification-of-Disaster-Related-Tweets-Parilla-Ferrer-Fernandez/f82e985ad5abc2f6f219f9cd83c248ebd132e3e4>

Schaaff, S. V. (2019, October 12). Lots of Americans have a fear of
flying. There are ways to overcome the anxiety disorder. *Washington
Post*.
<https://www.washingtonpost.com/health/lots-of-americans-have-a-fear-of-flying-there-are-way-to-overcome-the-anxiety-disorder/2019/10/11/d4746d84-d338-11e9-86ac-0f250cc91758_story.html>

Schlappig, B. (2022). *Ryanair's Hilarious, Rude, Savage Twitter Team*.
One Mile at a Time.
<https://onemileatatime.com/insights/ryanair-twitter/>

Wermuth, N. (1989). Moderating effects of subgroups in linear models.
*Biometrika, 76*(1), 81--92. <https://doi.org/10.1093/biomet/76.1.81>

Wu, L., Dodoo, N. A., & Choi, C.-W. (2023). Brand anthropomorphism on
Twitter: Communication strategies and consumer engagement. *Journal of
Product & Brand Management*, *ahead-of-print*(ahead-of-print).
<https://doi.org/10.1108/JPBM-12-2021-3787>
